### 2016-12-07 paper/chapters/gan.tex
normalizing flows -> VAE, oooops!
small fixes not worth an own commit

\begin{figure}[htb]
\centering
\includestandalone[width=\linewidth,mode=buildnew]{media/gan_conceptual}
  \caption{Conceptual figure of generative adversarial network}
  \label{fig:gan_a}
  \medskip
  \small
  Figure is illustrating the information and gradient flow in the GAN framework.\\
  \emph{data space} denotes the real-world data, which we aim to model.
  Dashed arrows denote the gradient flow.
\end{figure}

@@

\subsubsection{Normalizing Flows}
\label{ssub:gan_nf}

>>>>

\begin{figure}[htb]
\centering
\includestandalone[width=\linewidth,mode=buildnew]{media/gan_conceptual}
  \caption{Conceptual figure of generative adversarial network}
  \label{fig:gan_a}
  \medskip
  \small
  The above figure is illustrating the information and gradient flow in the GAN framework.\\
  \emph{data space} denotes the real-world data sampled from $p_{data}$, which we aim to model.
  Dashed arrows denote the gradient flow.
\end{figure}

@@

### 2016-12-07 paper/chapters/sigmoid_belief_nets.tex
small fixes not worth an own commit

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{SBN architecture}
  \label{fig:sbn_arch}
  \medskip
  \small
  Sigmoid Belief Network described as a acyclic directed graph where blue nodes indicate hidden variables while red nodes represent observed variables.
  Arrows show stochastic dependency. The dashed arrow indicates that it is possible in the original definition (and in the formula below) to have inter-layer dependencies but they are usually not modelled to simplify the architecture.
\end{figure}

\subsection{Learning}
\begin{figure}[htb]
\centering
\includestandalone[mode=buildnew]{media/sbn_node}
  \caption{Sigmoid Belief Net  architecture}
  \label{fig:sbn_node}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
$$

>>>>

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{SBN architecture}
  \label{fig:sbn_arch}
  \medskip
  \small
  Sigmoid Belief Network described as a acyclic directed graph where blue nodes indicate hidden variables while red nodes represent observed variables.
  Arrows show stochastic dependency. The dashed arrow indicates that it is possible in the original definition, even though most commonly the hidden variables are divided into layers.
\end{figure}

\subsection{Learning}
\begin{figure}[htb]
\centering
\includestandalone[mode=buildnew]{media/sbn_node}
  \caption{SBN node}
  \label{fig:sbn_node}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
$$
